---
output:
  html_document:
    toc: true
    toc_float: true
    theme: readable
    include:
      after_body: footer.html
    css: styles.css
---

```{r setup, echo=F}
knitr::opts_chunk$set(cache = TRUE)
setwd("~/zhen/scripts/zhenli.name/")
library(DT)
library(openxlsx)
```


<!-- In this page, you will find various useful resources related to single cell genomics, including: -->

<!-- * [List of human neocortex single cell RNA-seq datasets](#anchor1) -->
<!-- * [List of human organoid single cell RNA-seq datasets](#anchor2) -->
<!-- * List of mouse single cell RNA-seq datasets -->
<!-- * List of single cell genomics datasets -->

---

#Single cell RNA-seq Datasets {.tabset}

##Human 
<div style="padding: 20px">

```{r, echo=F}
dt <- read.xlsx("./single_cell_RNA-seq.xlsx",sheet = 1,rowNames = F)
datatable(dt, escape = F, options  = list(autoWidth = T))
```
</div>

##Mouse 
<div style="padding: 20px">

```{r, echo=F}
dt <- read.xlsx("./single_cell_RNA-seq.xlsx",sheet = 2,rowNames = F)
datatable(dt, escape = F, options  = list(autoWidth = T))
```
</div>

##Human organoid 
<div style="padding: 20px">
```{r, echo=F}
dt <- read.xlsx("./single_cell_RNA-seq.xlsx",sheet = 3,rowNames = F)
datatable(dt, escape = F, options  = list(autoWidth = T))
```
</div>

---

#Other resources
<div class="row">
<div class="column left"> 
<a href="http://www.brainspan.org/">BrainSpan</a>
</div>
<div class="column right">
<p>A large transcriptome database of the developing human brain.</p>
</div>
</div>
<div class="row">
<div class="column left">
<a href="http://hbatlas.org/mouseNCXtranscriptome/">Mouse Neocortical Transcriptome</a>
</div>
<div class="column right">
Atlas of gene expressions in mouse brain, including coding and some noncoding genes. It shows rough layer information.
</div>
</div>
<div class="row">
<div class="column left">
<a href="http://psychencode.org/">PsychENCODE</a>
</div>
<div class="column right">
Collection of data from the PsychENCODE consortium. This large dataset include RNA-seq, CHIP-seq, genomic sequencing and proteomics data of the developing human brain and numerous brain regions.
</div>
</div>
<div class="row">
<div class="column left">
<a href="https://david.ncifcrf.gov/">DAVID Gene Ontology</a>
</div>
<div class="column right">
Classic gene ontology analysis website.
</div>
</div>