---
# title: "info"
# author: "Zhen Li"
# date: "June 1, 2018"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, echo=F}
knitr::opts_chunk$set(cache = TRUE)
setwd("~/Scripts/my_web/")
library(DT)
library(openxlsx)
```


<!-- In this page, you will find various useful resources related to single cell genomics, including: -->

<!-- * [List of human neocortex single cell RNA-seq datasets](#anchor1) -->
<!-- * [List of human organoid single cell RNA-seq datasets](#anchor2) -->
<!-- * List of mouse single cell RNA-seq datasets -->
<!-- * List of single cell genomics datasets -->

---

<style>
.colored {
  background-color: #DDDDDD;
}
</style>

```{r, echo=F}
dt <- read.xlsx("./human_single_cell_RNA-seq_datasets.xlsx",sheet = 1,rowNames = F)
datatable(dt, escape = F, options  = list(autoWidth = T),)
```

#Human single cell RNA-seq datasets {#anchor1}
|Reference|Method|cDNA type|Age|# of cells|Source of cells|Seq Depth|# of genes per cell|
|:-------:|:----:|:-------:|:-:|:----------:|:-------------:|:--------:|:--------:|
|[Johnson](https://www.nature.com/articles/nn.3980)|FACS|Full-length(?)|16-17pcw|?|oRG|?|?|
|[Darmanis](http://www.pnas.org/content/112/23/7285)|C1|Full-length|14-16pcw;21-63y|466|TC & FC|2.8M|~4,000|
|[Lake](http://science.sciencemag.org/content/352/6293/1586.long)|snSeq(C1)|Full-length|51y|3227|6 Brodmann areas|8.3M|6159|
|[Pollen](https://doi.org/10.1016/j.cell.2015.09.004)|C1|Full-length|14-16pcw|393|VZ/SVZ|2.5M|3,099|
|[Nowakowski](http://science.sciencemag.org/content/358/6368/1318)|C1|Full-length|6-37pcw|4,261|Cortex|2.2M|2,403|
|[Zhong](https://www.nature.com/articles/nature25980)|Smartseq2|Full-length|6-24pcw|2394|PFC|?|2654|
|[Lake](https://www.nature.com/articles/nbt.4038)|Drop-seq|3'|22-49y|27906|Visual, frontal and cerebellum|~10000|719|
|[Fan](https://www.nature.com/articles/s41422-018-0053-3)|STRT|3'|22-23pcw|4,213|20+2 regions|2M|4,318|

---

#Mouse single cell RNA-seq datasets {#anchor2}
|Reference|Method|cDNA type|Age|# of cells|Source of cells|Seq Depth|# of genes per cell|
|:-------:|:----:|:-------:|:-:|:--------:|:-------------:|:-------:|:-----------------:|
|[Saraiva](https://www.nature.com/articles/srep18178)|C1|Full-length|P25|30|Olfactory sensory neurons|4.4M|4717|
|[Tasic](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4985242/)|SMARTer|Full-length|8wks|1,679|V1C|8.7M|7278|
|[Zeisel](http://science.sciencemag.org/content/347/6226/1138)|C1|5'|3-5wks|3,005|S1C & HIP|0.5M|4,500|
|[Macosko](https://www.sciencedirect.com/science/article/pii/S0092867415005498)|Drop-seq|3'|P14|44,808|Retina|?|?|
|[Rosenberg](http://science.sciencemag.org/content/360/6385/176)|SPLiT-seq|3'(?)|P2 & P11|156,049|4,497|
|[Dong](https://genomebiology.biomedcentral.com/articles/10.1186/s13059-018-1416-2)|STRT|3'(?)|E9.5-11.5|1,916|Multiple organs|0.43M UMI/cell|6,361|
|[han](https://www.sciencedirect.com/science/article/pii/S0092867418301168)|Microwell-seq|3'|E14.5|>400,000|Multiple organs|?|6,500|

---

#Human organoid single cell RNA-seq datasets {#anchor3}
|Reference|Method|cDNA type|Age|# of cells|Seq Depth|# of genes per cell|
|:-------:|:----:|:-------:|:-:|:--------:|:-------:|:-----------------:|
|[Quadrato](https://www.nature.com/articles/nature22047)|Drop-seq|3'|3 and 6mons|82291|?|?|



